Interactive Data Exploration with Smart Drill-Down (Extended Version)

### 2016-12-04 TableSummarization/journalVersion/smartDrillDown.tex
missing red color

\begin{lemma}\label{lemma:submodular}
For a given table $T$, the Score function over sets $S$ of rules, defined by the following is submodular:
$$\text{Score}(S) = \sum_{r \in S} MCount(r,S)W(r)$$
\end{lemma}
\papertext{\vspace{-10pt}}
\techreporttext{
\begin{proof}
Let $R(S)$ be the rule list obtained by sorting $S$ in descending weight order. For each tuple $t$, let $TOP(t,S)$ denote the first rule in rule-list $R(S)$ that covers $t$. By definition of $R(S)$, $r$ must also have the highest weight out of all rules in $S$ that cover $t$. Then $MCount(r,S)$ is simply $\sum_{t \in T : TOP(t,S) = r} 1$. Thus Score can be rewritten as:
$$\text{Score}(S) = \sum_{t \in T} W(TOP(t,S))$$
Now let $S \subsetneq S'$ and $s \notin S$. Then to prove submodularity, we simply need to prove that $$\text{Score}(S \cup \{s\}) - \text{Score}(S) \geq \text{Score}(S' \cup \{s\}) - \text{Score}(S')$$. We have
$\text{Score}(S \cup \{s\}) - \text{Score}(S) = \sum_{t \in T} W(TOP(t,S \cup \{s\})) - W(TOP(t,S))$ 
and an analogous equation for $S'$. Consider two cases: 
\begin{enumerate}
\item $W(TOP(t,S' \cup \{s\})) - W(TOP(t,S')) > 0$: This means $s$ covers $t$ and has higher weight than any rule in $S'$ that covers $t$. That is, $TOP(t,S' \cup \{s\}) = s$. Since $S \subseteq S'$, we must have $W(TOP(t,S')) \geq W(TOP(t,S))$, and also $TOP(t,S \cup \{s\}) = s$. Thus we have $W(TOP(t,S' \cup \{s\})) - W(TOP(t,S')) \leq W(TOP(t,S \cup \{s\})) - W(TOP(t,S))$.
\item $W(TOP(t,S' \cup \{s\})) - W(TOP(t,S')) = 0$: In this case, clearly 
$W(TOP(t,S' \cup \{s\})) - W(TOP(t,S')) \leq W(TOP(t,S \cup \{s\})) - W(TOP(t,S))$ since the latter is non-negative. 
\end{enumerate}
Either way, we have $W(TOP(t,S' \cup \{s\})) - W(TOP(t,S')) \leq W(TOP(t,S \cup \{s\})) - W(TOP(t,S))$, and summing over all $t \in T$ gives us 
$$\text{Score}(S \cup \{s\}) - \text{Score}(S) \geq \text{Score}(S' \cup \{s\}) - \text{Score}(S')$$
as required.
\end{proof}
}

>>>>

\begin{lemma}\label{lemma:submodular}
For a given table $T$, the Score function over sets $S$ of rules, defined by the following is submodular:
$$\text{Score}(S) = \sum_{r \in S} MCount(r,S)W(r)$$
\end{lemma}
\papertext{\vspace{-10pt}}
\techreporttext{
\begin{proof}
\mrj{
Let $R(S)$ be the rule list obtained by sorting $S$ in descending weight order. For each tuple $t$, let $TOP(t,S)$ denote the first rule in rule-list $R(S)$ that covers $t$. By definition of $R(S)$, $r$ must also have the highest weight out of all rules in $S$ that cover $t$. Then $MCount(r,S)$ is simply $\sum_{t \in T : TOP(t,S) = r} 1$. Thus Score can be rewritten as:
$$\text{Score}(S) = \sum_{t \in T} W(TOP(t,S))$$
Now let $S \subsetneq S'$ and $s \notin S$. Then to prove submodularity, we simply need to prove that $$\text{Score}(S \cup \{s\}) - \text{Score}(S) \geq \text{Score}(S' \cup \{s\}) - \text{Score}(S')$$. We have
$\text{Score}(S \cup \{s\}) - \text{Score}(S) = \sum_{t \in T} W(TOP(t,S \cup \{s\})) - W(TOP(t,S))$ 
and an analogous equation for $S'$. Consider two cases: 
\begin{enumerate}
\item $W(TOP(t,S' \cup \{s\})) - W(TOP(t,S')) > 0$: This means $s$ covers $t$ and has higher weight than any rule in $S'$ that covers $t$. That is, $TOP(t,S' \cup \{s\}) = s$. Since $S \subseteq S'$, we must have $W(TOP(t,S')) \geq W(TOP(t,S))$, and also $TOP(t,S \cup \{s\}) = s$. Thus we have $W(TOP(t,S' \cup \{s\})) - W(TOP(t,S')) \leq W(TOP(t,S \cup \{s\})) - W(TOP(t,S))$.
\item $W(TOP(t,S' \cup \{s\})) - W(TOP(t,S')) = 0$: In this case, clearly 
$W(TOP(t,S' \cup \{s\})) - W(TOP(t,S')) \leq W(TOP(t,S \cup \{s\})) - W(TOP(t,S))$ since the latter is non-negative. 
\end{enumerate}
Either way, we have $W(TOP(t,S' \cup \{s\})) - W(TOP(t,S')) \leq W(TOP(t,S \cup \{s\})) - W(TOP(t,S))$, and summing over all $t \in T$ gives us 
$$\text{Score}(S \cup \{s\}) - \text{Score}(S) \geq \text{Score}(S' \cup \{s\}) - \text{Score}(S')$$
as required.}
\end{proof}
}
